\section{Implementation} \label{sec:impl}

\packdrop was implemented as a load balancing strategy in \charm\footnote{Available at: \texttt{https://github.com/viniciusmctf/\\packdrop-code/tree/SBAC-Release}}, a parallel programming model that provides a \textit{load balancing framework} based on migration of its parallel, message-driven objects, the \textit{chares}~\cite{CharmLOTR,sc14charm}.
\textit{Chares} are mapped as \textit{tasks} to PEs and the \charm runtime system (RTS) provides the load information needed for our rescheduling strategy.

The \charm RTS allows for the desired asynchronous behavior of \packdrop.
It also provides the necessary reduction and quiescence detection mechanisms used in this implementation.
Reductions are used to evaluate the total number of chares and the average load in the system, while the quiescence detection is necessary to finalize the information propagation step of the algorithm.

\charm provides application-independent load balancing, which means that any application may use global rescheduling strategies implemented for this RTS.
This way, any of the available applications for \charm can be used to evaluate our strategy and compare it to other load balancers available for this RTS.

During load balancing in the \charm RTS, each instance of \packdrop runs as an individual chare.
Remote procedures in the algorithms ($\rightarrow$) were implemented as messages, exchanged between objects.
Reductions ($\Rightarrow$) used the RTS provided interface ({\small\texttt{CkReduction}}).
The \textit{three-way handshake}, necessary to acknowledge a $Send$, was implemented with message exchanges.
Finally, synchronization barriers in our algorithms use either \textit{quiescence detection} or reductions.

\subsection{Benchmarks} \label{sec:benchmarks}

We experimented our strategy with $2$ benchmarks that are publicly available for \charm.
The first one is a synthetic benchmark called \textit{LB Test}. 
It simulates work with a variety of communication topologies, such as ring, meshes and randomized patterns.
\textit{LB Test} is known to have a low migration cost, with light \textit{chares}, and most of its load bound to computation, instead of communication.

The second one is a MD mini-app called \textit{LeanMD}\footnote{Available at: \texttt{http://charmplusplus.org/miniApps}}.
This mini-app simulates the behavior of atoms and it mimics the force computation done in the state-or-the-art MD application NAMD, winner of the Golden Bell Award~\cite{grapevine}.
LeanMD uses geometric decomposition in a three-dimensional ($3$D) simulation space.
However, since the number of simulated atoms in each region affects the number of exchanged messages, it has an irregular and dynamic communication pattern, even though it respects the geometric distribution.

\subsection{Other schedulers}

We compare the performance of \packdrop to other strategies available on \charm.
More specifically, strategies that may be selected by \charm 's workload-aware \textit{Meta-balancer}~\cite{MenonPHD}.
An overall description of each one of these load balancing strategies is presented below:

\begin{itemize}
	\item \refinelb is a refinement-based strategy that tries to minimize the number of migrated \textit{tasks}, exchanging load among PEs.
This strategy is specially efficient if the system imbalance is low, and may not be able to deal with high imbalance due to its limited migration approach.
	\item \greedylb creates two heaps, one for \textit{tasks} (max-min) and one for PEs (min-max). 
Then, it assigns tasks to PEs, associating the most work-heavy tasks with the least loaded PEs.
This strategy provides a good load balance, but may incur in high migration overhead.
    \item \distributedlb, also known as \textit{Grapevine}, is a distributed strategy based on epidemic communication and probabilistic transfer of work.
   This strategy has good scalability, but does not perform as well as centralized ones in smaller scenarios.
   \item \dummylb, a centralized load balancer that does not remap tasks but still gathers system information as other centralized approaches.
   This is the representative of a scenario without load balancing.

\end{itemize}



